\\[2cm]
The concern for the safety of our property has become increasingly intense since acts which criminals practice robberies or thefts occur quite often. In the case of motor vehicles, the owner is powerless to prevent the crime, since a reaction can endanger your life and others that accompany it. In this situation, it is necessary to use some mechanism that allows the user to recover their property while minimizing the risks to your health and others.

This paper presents the development of a facing vehicle safety system using GPS which allows tracking in real time of the car through a web application. Besides tracking function , the system allows the blocking, or is, you can remotely and irrevocably turn off the car, preventing it from being damaged caused by aggressive driving of miscreants in escape attempts or even make new crimes. The combination of geographic location with the remote shutdown reduces the chances of damage to property and prevents the owner try to respond during a criminal act because it can rely on the aid system.

The solution is based on two main modules : a system of special purpose embedded in the car and a Web service responsible for receiving information, transmitting commands of lock/unlock and user interface. The development process used software engineering principles applied to embedded systems allowing mapping succinctly initial requirements and architecture. The use of UML in the design of embedded module assisted in defining the hardware components to be used and the method of communication with the Web service implementation. At the end of the field tests were performed and load simulations in Web service to detect and correct potential bottlenecks.


Keywords : GPS, GSM, Webservice, Embedded System
